---
title: "Presentation Test"
subtitle: "Learning⚔<br/>with xaringan"
author: "Geetanjli Rani"
institute: "RSCE, UCL"
date: "2024/20/01 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:  
    css: [default, rladies, rladies-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

Starting to Learn

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wiki Commo](https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

---
class: center, middle

# Learning xaringan

### I have no idea about his /ʃaː.'riŋ.ɡan/

---
class: inverse, center, middle

# Great Start for me, Yeah !

---

# Hello all

The MSc Urban Spatial Science **2023/24** classmates, we can types code chunks on between as below:

```{r eval=FALSE, tidy=FALSE}
remotes::install_github("yihui/xaringan")
```

--
We are recommended to use the hyperlinks in brackets as such [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Use single dash for bullet points
and footnotes as Presentation`;<sup>1</sup>

- More bullet points

- More More bullet points.

.footnote[
[1] single dot is used for footnotes.

[2] Also create hyperlinks in eg. footnote [#2](https://github.com/yihui/xaringan/issues/2).
]

---

class: inverse, middle, center

# Using xaringan

---
# xaringan

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```

See the help page `?xaringan::moon_reader` for all possible options that you can use.

---

# Left vs Right Pull

Some differences between left and right pull:

.pull-left[
1. Left is;

1. Left pull;

1. Trying left pull;
]

.pull-right[
1. Right is;

1. Righ pull;

1. Trying right pull;
]

---

# Math Expressions

I am trying writing a LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\gamma+\alpha$ renders $\gamma+\alpha$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# R Code

```{r comment='#'}
# I am trying a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
# I am trying to plot R plots
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```


---

# CSS

Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.

You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css). You can completely replace it with your own CSS files, or define new rules to override the default. See the help page `?xaringan::moon_reader` for more information.

---

# CSS

For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:

```css
@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
```

Then set the `css` option in the YAML metadata:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "ubuntu-mono.css"]
```

Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.

See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.

---

# CSS (with Sass)

**xaringan** also supports Sass support via **rmarkdown**. Suppose you want to use the same color for different elements, e.g., first heading and bold text. You can create a `.scss` file, say `mytheme.scss`, using the [sass](https://sass-lang.com/) syntax with variables:

```scss
$mycolor: #ff0000; 
.remark-slide-content > h1 { color: $mycolor; }
.remark-slide-content strong { color: $mycolor; }
```

Then set the `css` option in the YAML metadata using this file placed under the same directory as your Rmd:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "mytheme.scss"]
```

This requires **rmarkdown** >= 2.8 and the [**sass**](https://rstudio.github.io/sass/) package. You can learn more about **rmarkdown** and **sass** support in [this blog post](https://blog.rstudio.com/2021/04/15/2021-spring-rmd-news/#sass-and-scss-support-for-html-based-output) and in [**sass** overview vignette](https://rstudio.github.io/sass/articles/sass.html).

---

# Themes

Don't want to learn CSS? Okay, you can use some user-contributed themes. A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name. Below are some existing themes:

```{r, R.options=list(width = 70)}
names(xaringan:::list_css())
```

---

# Themes

To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,

```yaml
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
```

If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.org/en/2017/10/xaringan-themes).

---
class: inverse, middle, center
background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
background-size: contain

# Naruto

---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

# Sharingan

The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:

- the "Eye of Insight"

- the "Eye of Hypnotism"

I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>

.footnote[
[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.

[2] By comparison, bad presentations only put the audience to sleep.

[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
]

---

# Naruto terminology

The **xaringan** package borrowed a few terms from Naruto, such as

- [Sharingan](https://naruto.fandom.com/wiki/Sharingan) (写輪眼; the package name)

- The [moon reader](https://naruto.fandom.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)

- [Chakra](https://naruto.fandom.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)

- [Nature transformation](https://naruto.fandom.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)

- The [infinite moon reader](https://naruto.fandom.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)

- The [summoning technique](https://naruto.fandom.com/wiki/Summoning_Technique) (download remark.js from the web)

You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr/), and [R Markdown](https://rmarkdown.rstudio.com).
